%!TeX program = pdflatex
% Martin Fleischmann's Curriculum Vitae
% Email: martin@martinfleischmann.net
% Web: https://martinfleischmann.net/
% Repo: https://github.com/martinfleis/cv

\documentclass[12pt,a4paper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[UKenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{Martin Fleischmann}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {urban morphology, urban geography, software development, geographic data science},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}

    \begin{minipage}[t]{0.6\textwidth}
        \begin{flushleft}
            \textsuperscript{1}Urban and Regional Laboratory, Charles University, CZ \\
            \textsuperscript{2}Geographic Data Science Lab, University of Liverpool, UK \\
        \end{flushleft}
    \end{minipage}%
    %
    \begin{minipage}[t]{0.4\textwidth}
        \begin{flushright}
            \href{https://orcid.org/0000-0003-3319-3366}{0000-0003-3319-3366} \\
            citations: 483 (WoS) / 998 (GS) \\
            h-index: 10 / 12
        \end{flushright}
    \end{minipage}%


    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Architecture, University of Strathclyde, Glasgow, 2021 \\
                           \textit{The Urban Atlas: Methodological Foundation of a Morphometric Taxonomy of Urban Form}
        \item[MSc.]  \tab{}Urban Design, University of Strathclyde, Glasgow, 2017 \\
                           \textit{Measuring Urban Form: A Systematisation of Attributes for Quantitative Urban Morphology}

    \end{tablist}


    \section*{Academic Appointments}

    \begin{tablist}

        \item[2024--] \tab{}Charles University in Prague \\
                            Research Associate, Department of Social Geography and Regional Development

        \item[2023-24] \tab{}The Alan Turing Institute \\
                            Postdoctoral Research Associate \\

         \item[2022-23] \tab{}Charles University in Prague \\
                            Postdoctoral Researcher, Department of Social Geography and Regional Development

        \item[2020--22] \tab{}University of Liverpool \\
                            Research Associate, Department of Geography and Planning \\

    \end{tablist}

    \section*{Selected publications}

    \begin{tablist}

        \item[2024] \tab{}Fleischmann, M. and Arribas-Bel, D., \enquote{Decoding (urban) form and function using spatially explicit deep learning} \textit{Computers, Environment and Urban Systems} 112, 102147 \href{https://doi.org/10.1016/j.compenvurbsys.2024.102147}{doi:10.1016/j.compenvurbsys.2024.102147}

        \item[2023] \tab{}Fleischmann, M. \enquote{Clustergram: Visualization and diagnostics for cluster analysis}. \textit{Journal of Open Source Software} 8 (89), 5240. \href{https://doi.org/10.21105/joss.05240}{doi:10.21105/joss.05240}

        \item[2023] \tab{}Wang, J., Fleischmann, M., Venerandi, A., Romice, O., Kuffer, M., and Porta, S. \enquote{EO + Morphometrics: Understanding cities through urban morphology at large scale} \textit{Landscape and Urban Planning}, 233. \href{https://doi.org/10.1016/j.landurbplan.2023.104691}{doi:10.1016/j.landurbplan.2023.104691}

        \item[2022] \tab{}Arribas-Bel, D. and Fleischmann, M. \enquote{Spatial Signatures: Understanding (urban) spaces through form and function} \textit{Habitat International}, 128, (102641). \href{https://doi.org/10.1016/j.habitatint.2022.102641}{doi:10.1016/j.habitatint.2022.102641}

        \item[2022] \tab{}Fleischmann, M. and Arribas-Bel, D. \enquote{Geographical characterisation of British urban form and function using the spatial signatures framework} \textit{Scientific Data}, 9, (546). \href{https://doi.org/10.1038/s41597-022-01640-8}{doi:10.1038/s41597-022-01640-8}

        \item[2022] \tab{}Singleton, A., Arribas-Bel, D., Murray, J., and Fleischmann, M. \enquote{Estimating generalized measures of local neighbourhood context from multispectral satellite images using a convolutional neural network.} \textit{Computers, Environment and Urban Systems}, 95, 101802. \href{https://doi.org/10.1016/j.compenvurbsys.2022.101802}{doi:10.1016/j.compenvurbsys.2022.101802}

        \item[2021] \tab{}Fleischmann, M., Feliciotti, A., Romice, O. and Porta, S. \enquote{Methodological Foundation of a Numerical Taxonomy of Urban Form.} \textit{Environment and Planning B: Urban Analytics and City Science} 49 (4), 1283-1299. \href{https://doi.org/10.1177/23998083211059835}{doi:10.1177/23998083211059835}

        \item[2021] \tab{}Fleischmann, M., Feliciotti, A. and Kerr, W. \enquote{Evolution of urban patterns: urban morphology as an open reproducible data science.} \textit{Geographical Analysis} 54 (3). \href{https://doi.org/10.1111/gean.12302}{doi:10.1111/gean.12302}

        \item[2020] \tab{}Fleischmann, M., Romice, O. and Porta, S. \enquote{Measuring urban form: overcoming terminological inconsistencies for a quantitative and comprehensive morphologic analysis of cities.} \textit{Environment and Planning B: Urban Analytics and City Science} 48 (8), 2133-2150. \href{https://doi.org/10.1177/2399808320910444}{doi:10.1177/2399808320910444}

        \item[2020] \tab{}Fleischmann, M., Feliciotti, A., Romice, O. and Porta, S. \enquote{Morphological tessellation as a way of partitioning space: Improving consistency in urban morphology at the plot scale} \textit{Computers, Environment and Urban Systems} 80, 101441. \href{https://doi.org/10.1016/j.compenvurbsys.2019.101441}{doi:10.1016/j.compenvurbsys.2019.101441}

        \item[2019] \tab{}Fleischmann, M. \enquote{momepy: Urban Morphology Measuring Toolkit} \textit{Journal of Open Source Software} 4 (43), 1807. \href{https://doi.org/10.21105/joss.01807}{doi:10.21105/joss.01807}


    \end{tablist}

    \section*{Research income}

    \begin{tablist}

        \item[2024] \tab{}\textit{European Space Agency} \enquote{EuroFab: European Urban Fabric Classification Using Artificial Intelligence}, €250,000
        \item[2023] \tab{}\textit{Primus Research Programme, Charles University} \enquote{Influence of Socioeconomic and Cultural Factors on Urban Structure in Central Europe}, €325,000
        \item[2018] \tab{}\textit{University of Strathclyde} \enquote{John Anderson Research Award}, £60,000

    \end{tablist}

    \section*{Invited Talks and Keynotes}

    \begin{tablist}

        \item[2025] \tab{}\enquote{Open by Default} University College London, UK. Online. May 16.
        \item[2025] \tab{}\enquote{Urban science as a software} University of California, Berkeley. USA. Online. April 15.
        \item[2024] \tab{}\enquote{From a building to a region: Scalable morphology with urban morphometrics} International Seminar on Urban Morpho-Science. Nanjing, China. Oct 26
        \item[2024] \tab{}\enquote{The emergent structure of cities} 4th UrbanMetaMapping conference 'City Transition'. Saarbrücken, Germany. Sep 12.
        \item[2023] \tab{}\enquote{Open by Default} Oak Ridge National Laboratory, Oak Ridge. USA. Online. June 7.
        \item[2023] \tab{}\enquote{Open by Default} University of California, Santa Barbara. USA. Online. June 2.
        \item[2023] \tab{}\enquote{The emergent structure of urban form and function} Space Syntax Lab Seminars, UCL, London. Online. May 18.
        \item[2023] \tab{}\enquote{Urban morphology drawn and seen} NEtwoRks, Data, and Society. IT University of Copenhagen. Denmark. Online. Apr 26.
        \item[2021] \tab{}\enquote{Capturing the structure of cities with data science.} Spatial Data Science Conference 2021. Online. Oct 26.
        \item[2021] \tab{}\enquote{Spatial Signatures: Dynamic classification of the built environment.} Spatial Analytics and Data seminar series by University of Newcastle and University of Bristol. Online. Mar 30.

    \end{tablist}

\end{document}
